\begin{center}
	{\Huge System Requirements}
\end{center}
\setcounter{section}{0}
\section{System Requirements}

\textbf{Software Requirements:-}  Software requirements are the essential part to develop a project and we are using following softwares :-

\begin{enumerate}
	\item \textbf{Tensorflow} - Tensorflow is an open source software library for machine learning across a range of tasks, and developed by Google to meet their needs for systems capable of building and training neural networks to detect and decipher patterns and correlations, analogous to the learning and reasoning which humans use.
	
	Further requirements to run tensorflow with GPU support :-
	\begin{itemize}
		\item CUDA® Toolkit 8.0
		\item The NVIDIA drivers associated with CUDA Toolkit 8.0.
		\item cuDNN v5.1
		\item GPU card with CUDA Compute Capability 3.0 or higher
	\end{itemize}

	\item \textbf{NumPy}- NumPy is the fundamental package for scientific computing with Python. It contains among other things: a powerful N-dimensional array object. sophisticated (broadcasting) functions.
	
	\item \textbf{Python} - We need to have Python 3.0 installed in our machine in order to run our code and need an IDE for Python . Here we are using Pycharm as IDE for Python and we are developing this code in that.
	
	\item \textbf{TFLearn} - TFlearn is a modular and transparent deep learning library built on top of Tensorflow. It was designed to provide a higher-level API to TensorFlow in order to facilitate and speed-up experimentations, while remaining fully transparent and compatible with it.
	
	TFLearn features include:
	\begin{itemize}
		\item Easy-to-use and understand high-level API for implementing deep neural networks, with tutorial and examples.
		\item Fast prototyping through highly modular built-in neural network layers, regularizers, optimizers, metrics...
		\item Full transparency over Tensorflow. All functions are built over tensors and can be used independently of TFLearn.
		\item Powerful helper functions to train any TensorFlow graph, with support of multiple inputs, outputs and optimizers.
		\item Easy and beautiful graph visualization, with details about weights, gradients, activations and more...
		\item Effortless device placement for using multiple CPU/GPU.
		
	\end{itemize}

	\item \textbf{OpenCV} - OpenCV (Open Source Computer Vision) is a library of programming functions mainly aimed at real-time computer vision. The library is cross-platform and free for use under the open-source BSD license.
	
\end{enumerate}

\begin{flushleft}
	\textbf{Hardware Requirements}
\end{flushleft}
\begin{enumerate}
	\item TensorFlow programs typically run significantly faster on a GPU than on a CPU.Minimum requirement of GPU 2 GB memory.
	
	\item Octa - Core minimum processor required in order to process to process and analyse the data 
\end{enumerate}